HO unification from object language to meta language

### 2024-02-15 main.tex
update tex

% theorem prover and tc
Thanks to meta programming, it is feasible to express the equational theory of a
theorem prover, as noted in \cite{citeX, Y Z}, with the \ml serving as the
foundational infrastructure for this ecosystem. Proving a theorem, that is
solving a query using the jargon of logic programming consist in verifying if a
proposition is a logical consequence of a given set of assumption. The benefit
of of using a prologish verification style is that the proof resolution can be
automatized thanks to different search strategies, such as a depth first search
with backtracking. One of the main expression of this proof automation is
type-class resolution\cite{wadler89, sozeau08}. Type classes are a typing
structure to introduce ad-hoc polymorphism in functional programming languages.
In \coq, the use of type class has become a more and more used programming
style. Several are the libraries based on this machinery, we can site \stdpp and
\iris.

% embed tc in ml
One of the

>>>>

% theorem prover and tc
Thanks to meta programming, it is feasible to express the equational theory of a
theorem prover, as indicated in \cite{citeX, Y Z}, with the \ml serving as the
foundational infrastructure for this ecosystem. The process of proving a theorem, that is
solving a query using the jargon of logic programming consist in verifying if a
proposition is a logical consequence of a given set of assumption. The benefit
of of using a prologish verification style is that the proof resolution can be
automatized thanks to different search strategies, such as a depth first search
with backtracking. One prominent manifestation of this automated proof process is
type-class resolution\cite{wadler89, sozeau08}. Type classes serve as a typing
structure to introduce ad-hoc polymorphism in functional languages.
In \coq, the use of type class has increasingly become a programming
style. Numerous libraries, such as \stdpp and
\iris are built upon this machinery.

% embed tc in ml
The motivating example for this article is our investigation for an alternative
type-class solver for \coq in \elpi\todo{citation to elpi} through the \coqelpi
plugin. This plugin gives a deep embedding of \coq terms into \elpi syntax, but
challenges arise whe attempting to solve type-class goals represented into their
corresponding \elpi representation.
